Reduced diversity and increased specialzation of Alaska salmon fishermen:

### 2016-10-05 salmon/paper/salmon_paper.Rmd
simple model

```{r, echo=FALSE, fig.pos="placeHere", fig.cap="Time varying intercepts on estimated mean revenue, by permit."}
library(rstan)

# grab original data to look at permit names
diffdat = readRDS(file="../../salmon/data-generated/salmon.rds")
years = seq(min(diffdat$year), max(diffdat$year))
permits = levels(as.factor(diffdat$permit))

@@

ggplot(data=yearpermit) + 
  geom_ribbon(aes(x=year,ymin=b0_low,ymax=b0_hi),alpha=0.3) +
  geom_line(aes(x=year,y=b0)) + 
  facet_wrap(~permit) + xlab("Year") + ylab("Intercepts on mean")

@@

for(i in 1:nrow(df)) {
  tmp = est$g0_strategy[,df$permit[i]] + x1[df$diversity[i]] * (est$g_1[,df$year[i], df$permit[i]]+est$g1_str_yr_mu) +
    x2[df$diversity[i]] * (est$g_2[,df$year[i], df$permit[i]]+est$g2_str_yr_mu)# +
  #x3[df$diversity[i]] * (est$b_3[,df$year[i], df$permit[i]]+est$b3_str_yr_mu)
  df$pred[i] = median(tmp)
  df$low[i] = quantile(tmp,0.25)
  df$high[i] = quantile(tmp,0.75)
}

>>>>

```{r, echo=FALSE, fig.pos="placeHere", fig.cap="Time varying species composition and diversity, by permit. Species are colored as follows: yellow (chum), pink (sockeye), red (Chinook), green (coho), blue (pink salmon).", fig.height=3.2}
cfec <- feather::read_feather("../../portfolio/data-generated/salmon.feather")
cfec$year = as.numeric(substr(cfec$landdate, 1, 4))

library(dplyr)
# plot proportion of species landed by salmon permit
g1 = group_by(cfec[cfec$p_fshy=="S 01A" & cfec$spec %in% c("CHUM","COHO","SOCK","PINK","CHNK"),], year, spec, p_fshy) %>%
  summarize(p = sum(g_earn)) %>% group_by(year, p_fshy) %>% mutate(p = p/sum(p)) %>%
  ggplot(aes(year, p, group=spec, color = spec)) + geom_line() +  
  ylab("Species %") + xlab("") + ggtitle("S01A") + theme(legend.position="none")

g2 = group_by(cfec[cfec$p_fshy=="S 01E" & cfec$spec %in% c("CHUM","COHO","SOCK","PINK","CHNK"),], year, spec, p_fshy) %>%
  summarize(p = sum(g_earn)) %>% group_by(year, p_fshy) %>% mutate(p = p/sum(p)) %>%
  ggplot(aes(year, p, group=spec, color = spec)) + geom_line() +  
  ylab("Species %") + xlab("") + ggtitle("S01E") + theme(legend.position="none")

g3 = group_by(cfec[cfec$p_fshy=="S 01K" & cfec$spec %in% c("CHUM","COHO","SOCK","PINK","CHNK"),], year, spec, p_fshy) %>%
  summarize(p = sum(g_earn)) %>% group_by(year, p_fshy) %>% mutate(p = p/sum(p)) %>%
  ggplot(aes(year, p, group=spec, color = spec)) + geom_line() +  
  ylab("Species %") + xlab("") + ggtitle("S01K") + theme(legend.position="none")

g4 = group_by(cfec[cfec$p_fshy=="S 01M" & cfec$spec %in% c("CHUM","COHO","SOCK","PINK","CHNK"),], year, spec, p_fshy) %>%
  summarize(p = sum(g_earn)) %>% group_by(year, p_fshy) %>% mutate(p = p/sum(p)) %>%
  ggplot(aes(year, p, group=spec, color = spec)) + geom_line() +  
  ylab("Species %") + xlab("") + ggtitle("S01M") + theme(legend.position="none")

g5 = group_by(cfec[cfec$p_fshy=="S 03A" & cfec$spec %in% c("CHUM","COHO","SOCK","PINK","CHNK"),], year, spec, p_fshy) %>%
  summarize(p = sum(g_earn)) %>% group_by(year, p_fshy) %>% mutate(p = p/sum(p)) %>%
  ggplot(aes(year, p, group=spec, color = spec)) + geom_line() +  
  ylab("Species %") + xlab("") + ggtitle("S03A") + theme(legend.position="none")

g6 = group_by(cfec[cfec$p_fshy=="S 03E" & cfec$spec %in% c("CHUM","COHO","SOCK","PINK","CHNK"),], year, spec, p_fshy) %>%
  summarize(p = sum(g_earn)) %>% group_by(year, p_fshy) %>% mutate(p = p/sum(p)) %>%
  ggplot(aes(year, p, group=spec, color = spec)) + geom_line() +  
  ylab("Species %") + xlab("") + ggtitle("S03E") + theme(legend.position="none")

dat.diff = readRDS(file="../../portfolio/data-generated/cfec-diff-for-modeling.rds")
dat.diff = dat.diff[which(dat.diff$revenue >= 10000 & dat.diff$revenue.prev >= 10000), ]
dat.salmon = dat.diff[dat.diff$strategy_permit%in%c("S01A", "S01E", "S01K", "S03A", "S03E","S01M"),]

h1 = group_by(dat.salmon[dat.salmon$strategy_permit=="S01A",], year, strategy_permit) %>%
  summarize(meanDiv = mean(specDiv), low = quantile(specDiv,0.25), upp = quantile(specDiv,0.75)) %>%
  ggplot(aes(year, meanDiv)) + geom_line() + 
  geom_ribbon(aes(ymin= (low), ymax= (upp)), alpha=0.4) + ylab("Diversity") + xlab("") + theme(legend.position="none")

h2 = group_by(dat.salmon[dat.salmon$strategy_permit=="S01E",], year, strategy_permit) %>%
  summarize(meanDiv = mean(specDiv), low = quantile(specDiv,0.25), upp = quantile(specDiv,0.75)) %>%
  ggplot(aes(year, meanDiv)) + geom_line() + 
  geom_ribbon(aes(ymin= (low), ymax= (upp)), alpha=0.4) + ylab("Diversity") + xlab("") + theme(legend.position="none")

h3 = group_by(dat.salmon[dat.salmon$strategy_permit=="S01K",], year, strategy_permit) %>%
  summarize(meanDiv = mean(specDiv), low = quantile(specDiv,0.25), upp = quantile(specDiv,0.75)) %>%
  ggplot(aes(year, meanDiv)) + geom_line() + 
  geom_ribbon(aes(ymin= (low), ymax= (upp)), alpha=0.4) + ylab("Diversity") + xlab("") + theme(legend.position="none")

h4 = group_by(dat.salmon[dat.salmon$strategy_permit=="S01M",], year, strategy_permit) %>%
  summarize(meanDiv = mean(specDiv), low = quantile(specDiv,0.25), upp = quantile(specDiv,0.75)) %>%
  ggplot(aes(year, meanDiv)) + geom_line() + 
  geom_ribbon(aes(ymin= (low), ymax= (upp)), alpha=0.4) + ylab("Diversity") + xlab("") + theme(legend.position="none")

h5 = group_by(dat.salmon[dat.salmon$strategy_permit=="S03A",], year, strategy_permit) %>%
  summarize(meanDiv = mean(specDiv), low = quantile(specDiv,0.25), upp = quantile(specDiv,0.75)) %>%
  ggplot(aes(year, meanDiv)) + geom_line() + 
  geom_ribbon(aes(ymin= (low), ymax= (upp)), alpha=0.4) + ylab("Diversity") + xlab("") + theme(legend.position="none")

h6 = group_by(dat.salmon[dat.salmon$strategy_permit=="S03E",], year, strategy_permit) %>%
  summarize(meanDiv = mean(specDiv), low = quantile(specDiv,0.25), upp = quantile(specDiv,0.75)) %>%
  ggplot(aes(year, meanDiv)) + geom_line() + 
  geom_ribbon(aes(ymin= (low), ymax= (upp)), alpha=0.4) + ylab("Diversity") + xlab("") + theme(legend.position="none")

gridExtra::grid.arrange(g1, g2, g3, h1, h2, h3, nrow=2)
```

```{r, echo=FALSE, fig.pos="placeHere", fig.cap="Time varying species composition and diversity, by permit.", fig.height=3.2} 
gridExtra::grid.arrange(g4, g5, g6, h4, h5, h6, nrow=2)
```

```{r, echo=FALSE}
library(rstan)
```

```{r, echo=FALSE, fig.pos="placeHere", fig.cap="Time varying intercepts on estimated mean revenue, by permit.", eval=FALSE}
# grab original data to look at permit names
diffdat = readRDS(file="../../salmon/data-generated/salmon.rds")
years = seq(min(diffdat$year), max(diffdat$year))
permits = levels(as.factor(diffdat$permit))

@@

ggplot(data=yearpermit) + 
  geom_ribbon(aes(x=year,ymin=b0_low,ymax=b0_hi),alpha=0.3) +
  geom_line(aes(x=year,y=b0)) + 
  facet_wrap(~permit) + xlab("Year") + ylab("Intercepts on mean")
```

@@

for(i in 1:nrow(df)) {
  tmp = est$g0 + est$g0_strategy[,df$permit[i]] + x1[df$diversity[i]] * (est$g_1[,df$year[i], df$permit[i]]+est$g1_str_yr_mu) +
    x2[df$diversity[i]] * (est$g_2[,df$year[i], df$permit[i]]+est$g2_str_yr_mu)# +
  #x3[df$diversity[i]] * (est$b_3[,df$year[i], df$permit[i]]+est$b3_str_yr_mu)
  df$pred[i] = median(tmp)
  df$low[i] = quantile(tmp,0.25)
  df$high[i] = quantile(tmp,0.75)
}
